A Theory for Migration of Information Systems

### 2022-09-05 2022 Migration/articleMigration.tex
WIP

	We can now define the notion of dataset.
	Let	$\concepts$ be a set of concept symbols,
	let $\isa$ be a partial order on $\concepts$,
	let $\rels$ be a set of relations,
	let $\atoms$ be a set of atoms,
	and let $\inst$ be a relation $\atoms\times\concepts$ that represents the instance relation between concepts and atoms,
\begin{definition}[dataset]
	\label{def:dataset}
	\item A dataset is a tuple $\la\atoms,\concepts,\inst,\isa,\rels,\triples\ra$ with
	\begin{eqnarray}
		\forall a\in\atoms\ \exists A\in\concepts&:&a\ \inst\ A\\
		\forall A,B\in\concepts, a\in\atoms&:&A\isa B\wedge a\ \inst\ A\ \Rightarrow\ a\ \inst\ B\\
		\forall r\in\rels&:&\src{r}\in\concepts\ \wedge\ \tgt{r}\in\concepts\\
		\forall\triple{a}{r}{b}\in\triples&:&r\in\rels\ \wedge\ a\ \inst\ \src{r}\ \wedge\ b\ \inst\ \tgt{r}\\
	\end{eqnarray}
\end{definition}

\subsection{Information Systems}
\label{sct:Information Systems}
	Information systems process information from many different users, each with their own tasks and responsibilities.
	Users work from different locations and on different moments.
	This collective use serves a purpose which we loosely call "the business".
	As a consequence, the data in an information system changes continually.
	To preserve meaning, users are trying to maintain semantic constraints on the data.
	Before defining information systems for the purpose of data migration,
	let us first define the constituent notions role and constraint, which are part of that definition.

@@

	Note that the signature of $u$ does not depend on the population, whereas the violation set of $u$ may be different for every $\triples$.
	Since $\triples$ changes continuallyin an information system, the violations are changing along.

>>>>

	We can now define the notion of dataset.
	Let	$\concepts$ be a set of concept symbols,
	let $\isa$ be a partial order on $\concepts$,
	let $\rels$ be a set of relations,
	let $\atoms$ be a set of atoms,
	and let $\inst$ be a relation $\atoms\times\concepts$ that represents the instance relation between concepts and atoms,
\begin{definition}[dataset]
	\label{def:dataset}
	\item A dataset is a tuple $\la\atoms,\concepts,\inst,\isa,\rels,\triples\ra$ with
	\begin{eqnarray}
		\forall a\in\atoms\ \exists A\in\concepts&:&a\ \inst\ A\\
		\forall A,B\in\concepts, a\in\atoms&:&A\isa B\wedge a\ \inst\ A\ \Rightarrow\ a\ \inst\ B\\
		\forall r\in\rels&:&\src{r}\in\concepts\ \wedge\ \tgt{r}\in\concepts\\
		\forall\triple{a}{r}{b}\in\triples&:&r\in\rels\ \wedge\ a\ \inst\ \src{r}\ \wedge\ b\ \inst\ \tgt{r}
	\end{eqnarray}
\end{definition}

\subsection{Information Systems}
\label{sct:Information Systems}
	Information systems process information from many different users,
	all with their own tasks and responsibilities,
	and all working from different locations and on different moments.
	This collective use serves a purpose which we loosely call "the business".
	As a consequence, the data in an information system changes continually.
	To preserve meaning, users are trying to maintain semantic constraints on the data.
	So, let us first define the constituent notions role and constraint before defining information systems proper.

@@

	Note that the signature of $u$ does not depend on the population, whereas the violation set of $u$ may be different for every $\triples$.
	Since $\triples$ changes continually in an information system, the violations are changing along.
